---
title: "Spotify US Visualization"
author: "Mark Gallo"
due date: '2019-12-13'
output:
  html_notebook:
    toc: yes
  html_document:
    highlight: textmate
    theme: flatly
    toc: yes
 
---


```{r}
library(httr)
library(jsonlite)
library(xml2)
library(XML)
library(stringr)
library(purrr)
library(dplyr)
library(stringr)
library(sylly.en)
library(data.table)
library(curl)

library(leaflet)
library(tidyverse)
library(varhandle)
library(shiny)
library(RColorBrewer)
library(tibble)
library(shinydashboard)
library(flexdashboard)
library(DT)
library(sp)
library(reprex)
library(usmap)
```

```{r}
usethis::edit_r_environ()
```

### Get Access to Spotify 
#### Source Code: https://github.com/charlie86/spotifyr
#### Insert Spotify API Client / Secret 

```{r}
get_spotify_access_token <- function(client_id =Sys.getenv('SPOTIFY_CLIENT_ID'), client_secret = Sys.getenv('SPOTIFY_CLIENT_SECRET')) {

    post <- RETRY('POST', 'https://accounts.spotify.com/api/token',
                 accept_json(), authenticate(client_id, client_secret),
                 body = list(grant_type = 'client_credentials'),
                 encode = 'form', httr::config(http_version = 2)) %>% content

    if (!is.null(post$error)) {
        stop(str_glue('Could not authenticate with given Spotify credentials:\n\t{post$error_description}'))
    }

    access_token <- post$access_token

    return(access_token)
}

```


```{r}
access_token <- get_spotify_access_token()
```

#### Source Code: https://github.com/charlie86/spotifyr
#### Insert Spotify API Client / Secret 

```{r}
get_spotify_authorization_code <- function(client_id = Sys.getenv('SPOTIFY_CLIENT_ID'), client_secret = Sys.getenv('SPOTIFY_CLIENT_SECRET'), scope = spotifyr::scopes) {
    endpoint <- oauth_endpoint(authorize = 'https://accounts.spotify.com/authorize', access = 'https://accounts.spotify.com/api/token')
    app <- oauth_app('spotifyr', client_id, client_secret)
    oauth2.0_token(endpoint = endpoint, app = app, scope = scope)
}
```

#### Source Code: https://github.com/charlie86/spotifyr
#### Inserty Spotify Client / Client  

```{r}
get_playlist <- function(playlist_id, fields = NULL, market = NULL, authorization = get_spotify_access_token(Sys.getenv('SPOTIFY_CLIENT_ID'),Sys.getenv('SPOTIFY_CLIENT_SECRET'))) {
    base_url <- 'https://api.spotify.com/v1/playlists'
    url <- str_glue('{base_url}/{playlist_id}')
    params <- list(
        fields = paste(fields, collapse = ','),
        market = market,
        access_token = authorization
    )
    res <- RETRY('GET', url, query = params, encode = 'json')
    stop_for_status(res)
    res <- fromJSON(content(res, as = 'text', encoding = 'UTF-8'), flatten = TRUE)
    return(res)
}

```

### Generate Data
#### Generate Data Frames of Artists on Spotify Playlists

```{r}
spotUSTop50 <- get_playlist("37i9dQZEVXbLRQDuF5jeBp")
spotUSTopRap <- get_playlist("37i9dQZF1DX0XUsuxWHRQd")
spotUSTopCounty <- get_playlist("37i9dQZF1DX1lVhptIYRda")

```

```{r}

top50sp <- spotUSTop50$tracks$items$track.album.artists
topUSRap <- spotUSTopRap$tracks$items$track.album.artists
topUSCountry <- spotUSTopCounty$tracks$items$track.album.artists
```


```{r}
US_Top50_Artists_Spotify <- as.data.frame(unlist(lapply(top50sp,function(x) x[1,3])))
US_Top50_Artists_Spotify<-setNames(US_Top50_Artists_Spotify, "US Top 50 Spotify")

US_TopRap_Artists_Spotify <- as.data.frame(unlist(lapply(topUSRap,function(x) x[1,3])))
US_TopRap_Artists_Spotify<-setNames(US_TopRap_Artists_Spotify, "US Top Rap Spotify")

US_TopCountry_Artists_Spotify <- as.data.frame(unlist(lapply(topUSCountry,function(x) x[1,3])))
US_TopCountry_Artists_Spotify<-setNames(US_TopCountry_Artists_Spotify, "US Top Country Spotify")

```

### Function To Expidite Process
#### The function requires a Spotify Playlist Code as a String (can be found on Spotify Web Player @ end of URL)

```{r}

getPlaylistArtist <- function(x){
  gp <- get_playlist(x)
  tg <- gp$tracks$items$track.album.artists
  uts <- as.data.frame(unlist(lapply(tg,function(y) y[1,3])))
  futs <- setNames(uts, "Artists")
  return(futs)
}

```

#Example of a playlist Get - Returns a data frame 

```{r}
playlistGet <- getPlaylistArtist("37i9dQZEVXbLRQDuF5jeBp")
```


### Access Seat Geek 

```{r}
sgURL <- "https://api.seatgeek.com/2/events?"
```



```{r}

query_params <- list("client_id" = Sys.getenv('SEATGEEK_CLIENT_ID'), "performers.slug" = "billie-eilish")
sgGet <- GET(sgURL, query = query_params)
sgData <- fromJSON(content(sgGet, "text"))

```

### Function to obtain performance data from those on the playlist, as determined by SeatGeek
#### Insert SeatGeek API Client 


```{r}

sgPerfroamnce <-  function(p = "Lil-Baby", client_id = Sys.getenv('SEATGEEK_CLIENT_ID')){
 
  query_params <- list("client_id" = client_id, "performers.slug" = p )
  sgGet <- GET(sgURL, query = query_params)
  sgData <- fromJSON(content(sgGet, "text"))

  if(is.null(sgData$events$venue$city[1])){
    sgData$events$venue$city[1] = NA
    sgData$events$venue$state[1] = NA
    sgData$events$datetime_local[1] = NA
    sgData$events$stats$average_price[1] = NA 
    sgData$events$venue$name[1] = NA
    sgData$events$venue$location$lat[1] = NA
    sgData$events$venue$location$lon[1] = NA
    sgData$events$popularity[1] = NA
    sgData$events$stats$lowest_price[1] = NA
    
  }

perfData <- data.frame(cbind(sgData$events$venue$city[1],sgData$events$venue$state[1],sgData$events$datetime_local[1],sgData$events$stats$average_price[1],sgData$events$venue$name[1],sgData$events$venue$location$lat[1], sgData$events$venue$location$lon[1], sgData$events$popularity[1], sgData$events$stats$lowest_price[1]))

perfData <- cbind(p, perfData)
#setNames(perfData, c("Artist","City","State", "Data & Time", "Avg Price", "lat","lon" ))


}
```

```{r}
View(sgPerfroamnce("My Chemical Romance",Sys.getenv('SEATGEEK_CLIENT_ID')))
```


### Function to make table out all upcomming performances by artists in given playlist 
#### Insert SeatGeek Client ID 

```{r}
data <- data.table()
makeTable <- function(artist_data, client_id = Sys.getenv('SEATGEEK_CLIENT_ID')){
 
 
   for(a in artist_data){
    dash <- (str_replace_all(a, " ", "-"))
    for(d in dash){
      data <- rbind(data, sgPerfroamnce(d,client_id))
    }
    data <-setNames(data, c("Artist","City","State", "Data & Time", "Avg Price","Venue","lat","lng", "Popularity", "Lowest Price" ))
    return(data)
  }
}
```

#Make table given out of function of getting artists from given spotify id
Pop, Rap, and Country come included with the dashboard 

#### Insert SeatGeek API Client 


```{r}

topPop <- makeTable(getPlaylistArtist("37i9dQZEVXbLRQDuF5jeBp"), Sys.getenv('SEATGEEK_CLIENT_ID'))
topRap<- makeTable(getPlaylistArtist("37i9dQZF1DX0XUsuxWHRQd"),Sys.getenv('SEATGEEK_CLIENT_ID'))
topCountry <- makeTable(getPlaylistArtist("37i9dQZF1DX1lVhptIYRda"),Sys.getenv('SEATGEEK_CLIENT_ID'))


```


### Gather Data into groups by genre and combine to one Data Frame to be accessed when using drop down selection 

```{r}
pop <- topPop[complete.cases(topPop), ]

pop$Playlist <- "Pop"
rap <- topRap[complete.cases(topRap),]
rap$Playlist <- "Rap"
country <- topCountry[complete.cases(topCountry),]
country$Playlist <- "Country"


allgenre <- rbind(pop,rap,country)
#colnames(allgenre)[which(names(allgenre) == "State")] <- "state"
colnames(allgenre)[which(names(allgenre) == "Data & Time")] <- "Date & Time"
colnames(allgenre)[which(names(allgenre) == "State")] <- "state"
allgenre$`Avg Price` <- unfactor(allgenre$`Avg Price`)
allgenre$`Lowest Price` <-unfactor(allgenre$`Lowest Price`)
allgenre <- unique(allgenre[,c("Artist", "City", "state", "Avg Price", "Date & Time", "Lowest Price", "Playlist" )])
allgenre
```


### Adding a new playlist to the dashboard, use gatherAll with Spotify Playlist ID
#### change gat$genre (Line 277) and the genres vector (Line 297) to have the same name 
#### Insert SeatGeek Client ID 

```{r}
gatherAll <- function(x, client_id = Sys.getenv('SEATGEEK_CLIENT_ID')){
  u <- makeTable(getPlaylistArtist(x), client_id)
  gat <- u[complete.cases(u), ]
  gat$Playlist <- "MG Top Songs 2019"
  allgenre <- rbind(pop,rap,country,gat)
  colnames(allgenre)[which(names(allgenre) == "Data & Time")] <- "Date & Time"
  colnames(allgenre)[which(names(allgenre) == "State")] <- "state"
  allgenre <- unique(allgenre[,c("Artist", "City", "state", "Avg Price", "Date & Time", "Lowest Price", "Playlist" )])
  allgenre$`Avg Price` <- unfactor(allgenre$`Avg Price`)
  allgenre$`Lowest Price` <- unfactor(allgenre$`Lowest Price`)
  return(allgenre)
}
```

```{r}
allgenre <- gatherAll("37i9dQZF1Etmtc0GVuIsZH", Sys.getenv('SEATGEEK_CLIENT_ID'))
```



```{r}

PopAv <- allgenre %>% filter(Playlist == "Pop") %>% group_by(state) %>% summarise(round(mean(`Avg Price`)))
PopAv <- setNames(PopAv, c("state", "Price"))
PopAv$name <- "PopAvgPrices"

PopLow <- allgenre %>% filter(Playlist == "Pop") %>% group_by(state) %>% summarise(round(mean(`Lowest Price`)))
PopLow <- setNames(PopLow, c("state", "Price"))
PopLow$name <- "PopLowPrices"

RapAv <- allgenre %>% filter(Playlist == "Rap") %>% group_by(state) %>% summarise(round(mean(`Avg Price`)))
RapAv <- setNames(RapAv, c("state", "Price"))
RapAv$name <- "RapAvgPrices"

RapLow <- allgenre %>% filter(Playlist == "Rap") %>% group_by(state) %>% summarise(round(mean(`Lowest Price`)))
RapLow <- setNames(RapLow, c("state", "Price"))
RapLow$name <- "RapLowPrices"

CountryAv <- allgenre %>% filter(Playlist == "Country") %>% group_by(state) %>% summarise(round(mean(`Avg Price`)))
CountryAv <- setNames(CountryAv, c("state", "Price"))
CountryAv$name <- "CountryAvgPrices"

CountryLow <- allgenre %>% filter(Playlist == "Country") %>% group_by(state) %>% summarise(round(mean(`Lowest Price`)))
CountryLow <- setNames(CountryLow, c("state", "Price"))
CountryLow$name <- "CountryLowPrices"

allMeans <- rbind(PopAv, PopLow, RapAv, RapLow, CountryAv, CountryLow)

```


```{r}
chartData <- function(getname = "MG Top Song 2019", sortBy = ""){
  
  if(sortBy == "Avg Price"){
  topdata <- allgenre %>% filter(Playlist == getname) %>% group_by(state) %>% summarise(round(mean(`Avg Price`)))
  topdata <- setNames(topdata, c("state", "Price"))
  topdata$name <- paste(getname, "Avg")
  
  }
  
  if(sortBy == "Lowest Price"){
  topdata <- allgenre %>% filter(Playlist == getname) %>% group_by(state) %>% summarise(round(mean(`Lowest Price`)))
  topdata <- setNames(topdata, c("state", "Price"))
  topdata$name <- paste(getname, "Low")
  
  }
  allMeans <- rbind(PopAv, PopLow, RapAv, RapLow, CountryAv, CountryLow, topdata)
  return(allMeans)
}

```
 
### Once a new playlist has been added to the data frame this funtion makes it simple to allow graphical analysis to be run
 
```{r}
allMeansMG <- chartData("MG Top Songs 2019", "Lowest Price")
```

#Dashboard


```{r}

genres <- c("Pop", "Rap", "Country", "MG Top Songs 2019")
pricing <- c("PopAvgPrices", "PopLowPrices","RapAvgPrices", "RapLowPrices", "CountryAvgPrices", "CountryLowPrices", "MG Top Songs 2019 Low")

bins <- c(0, 10, 20, 50, 100, 200, 500, 1000, Inf)
pal <- colorBin("Greens", domain = c(0,2000), bins = bins)

ui <- dashboardPage(
  skin = "green",
  dashboardHeader(title = "Concert Ticket Prices Spotify & Seat Geek", titleWidth = 400),
  dashboardSidebar(selectInput("genre", label = "Choose Playlist",choices = genres, selected = "Pop")),
  
  
  dashboardBody(
    
     fluidRow(column(width = 4, box(width = NULL, status = "warning", uiOutput("pricing"), selectInput("pricing", label = "Sort Graphs By:",choices = pricing, selected = "RapAvgPrices")))),
    fluidRow(downloadButton('downloadData', 'Download Playlist CSV')),
    fluidRow(column(width = 12, box(width = NULL, splitLayout(cellWidths = c("50%", "50%") , plotOutput("plot"), plotOutput("barplot"))),
                    box(width = NULL, dataTableOutput(outputId = "summary_table")))),
    
    
    #selectInput("genre", label = "Genre",choices = genres, selected = "Pop")),
    #fluidRow(column(widthbox(width = 9, dataTableOutput(outputId = "summary_table"))),
    #fluidRow(textOutput(outputId = "genre_shp"))),
  )
  
  
  
)
server <- function(input, output, session){
  
  
  
  #text <- reactive({input$genre})
  #text2 <- reactive({text()})
  
  
  
   #renderLeaflet({genre_shp <- Allgenre[Allgenre$genre == input$genre,]})
  
  genre_shp <- reactive(allgenre[allgenre$Playlist == input$genre,])
  
  
  #allgenre$`Avg Price` allgenre$`Lowest Price`
    
  pricing_shp <- reactive(allMeansMG[allMeansMG$name == input$pricing,])
    
    
   
  
 
  #labels <- reactive({sprintf(
  #"<strong>%s</strong><br/>Average Price: $%g <br/>%s </br> %s, %s <br/> %s ",
  #genre_shp()$Artist, genre_shp()$`Avg Price`, genre_shp()$Venue, genre_shp()$City, genre_shp()$name, dataMap$`Data & Time`
#) %>% lapply(htmltools::HTML)})
    
  
  
  #output$mymap <- renderLeaflet({
  
  #leaflet(SpatialPolygons(genre_shp()))%>%
  #setView(-96, 37.8, 4) %>%
  #addProviderTiles("MapBox", options = providerTileOptions(
   # id = "mapbox.light",
  #  accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>%
  #addPolygons(
  #  fillColor = ~pal(genre_shp()$`Avg Price`),
   # weight = 2,
    #opacity = 1,
    #color = "white",
    #dashArray = "3",
    #fillOpacity = 0.7,
    #highlight = highlightOptions(
     # weight = 5,
      #color = "#666",
      #dashArray = "",
      #fillOpacity = 0.7,
      #bringToFront = TRUE),
    #label = labels,
    #labelOptions = labelOptions(
     # style = list("font-weight" = "normal", padding = "3px 8px"),
      #textsize = "15px",
      #direction = "auto")) %>%
  #addLegend(pal = pal, 
   #         values = genre_shp()$`Avg Price`, opacity = 0.7, title = NULL,
  #  position = "bottomright")
  #})
    
  
   output$summary_table <- renderDataTable(data.frame(genre_shp()))
   
   #Source: https://shiny.rstudio.com/reference/shiny/latest/downloadButton.html

   output$downloadData <- downloadHandler(
    filename = function() { 
      paste(input$genre,"MusicData", '.csv', sep='')
      },
    content = function(file) {
      write.csv(genre_shp(), file)
    })
   
    output$plot<-renderPlot({
      
    plot_usmap(data = pricing_shp(), values = "Price", color = "white") + 
  scale_fill_continuous(low = "#C9E6B2", high = "#1ED761", name = "Ticket Prices (USD)", label = scales::comma)+ 
  theme(legend.position = "right",legend.background = element_rect("white"),
        legend.box.background =   element_rect())+
        labs(title = paste(input$pricing, "For Concert Tickets Across US"), subtitle = "As According to Spotify & SeatGeek")})

   
   output$barplot <-renderPlot({
     ggplot(data = pricing_shp(),  aes(x = state, y = `Price` ))+ 
              geom_bar(stat = "identity", fill = "#1ED761")+
              ggtitle(paste(input$pricing, "of Concert Tickets on SeatGeek By State"))
   })
  

}
shinyApp(ui=ui, server = server)



```










